Corporate Security Solutions for BYOD:\\ A Novel User-Centric and Self-Adaptive System

### 2015-06-25 MUSES_vs_BYOD_solutions.tex
Changing introduction of 4.3 section

As previously stated, one of the main features of this system is the self-adaptation (to the user and context), of the set of Corporate Security Rules (specification of the ISPs), that it is be able to perform. 
To this end, the \textit{MusKRS} module is run asynchronously in the server (once a day or every X hours) and it is in charge of analysing all the gathered information (events, context, user-related data), and adapting or refining the security rules. The refinement (improvement)  has as aim to better deal with these events, optimizing the current set of rules (removing redundant or non-useful rules, for instance), and even trying to predict future threats due to the user's behaviour.

This procedure is be composed by two main steps: first, a Data Mining (DM) \cite{DataMining_Lee01} + Machine Learning (ML) \cite{MachineLearning_Bishop06} process is performed (in the \textit{Data Miner} sub-component);  second, a refinement and inference process  is done (in the \textit{Knowledge Compiler} sub-component), considering the data `extracted' in the first step, by means of Computational Intelligence (CI) techniques.
It should be noticed that part of the refinement (or adaptation) of the security rules is made using simpler methods, such as generalisation or specialisation of rules, for instance. Then, other parts of the process can be conducted using CI.

Another important fact is that MUSES  counts with a human controller, normally the Chief Security Officer (CSO) of the company, who  supervises the system activity by means of logs or feedback messages. Thus, adapted and inferred security rules are not, in principle, directly added to the current set of rules. Instead, they  are proposed as draft rules to this controller, in order that he/she can accept them if they are interesting and correct. The system  is able to `learn' from this decisions, so after a so-called training or `warm up' period, the rules can be directly accepted (included in the set) or rejected autonomously by the MusKRS.

The following sections describe these processes: first focusing on DM techniques to be used both automatically by the MusKRS, and as a kind of decision-aid and monitoring tool for the CSO; second, the CI techniques are explained, mainly focusing in Evolutionary Computation (EC) \cite{EAs_Back96} approaches, since these methods perform very well, and have been widely used in security-based environments for solving security issues, such as the intrusion detection \cite{GA_intrusion-majeed}, the design and evaluation of security protocols \cite{GP_intrusion-lu,GA_networksecurity-zarza}, or the optimisation of different aspects related with security: IT security costs \cite{EAs_securitycosts-kirta}, and cryptographic protocols \cite{GA_cryptographicprotocols-zarza2}, among others.

>>>>

The self-adaptation, to the user and context, of the set of Corporate Security Rules is one of the main features of this MUSES system.
To this end, the \textit{MusKRS} module is in charge of analysing all the gathered events, context, and user-related data. Then it processes the data and adapts or refines the security rules. This refinement is meant as an improvement of the existing security rules, and it aim is to deal with new, possibly insecure, events. As a result, a set of optimisations and additions to the set of security rules are proposed to the Chief Security Officer (CSO) of the company.

This procedure is composed by two main steps: first, a Data Mining (DM) \cite{DataMining_Lee01} + Machine Learning (ML) \cite{MachineLearning_Bishop06} process is performed in the \textit{Data Miner} sub-component; second, a refinement and inference process is done in the \textit{Knowledge Compiler} sub-component, using the data that was extracted in the first step, and by means of Computational Intelligence (CI) techniques.
The refinement, or adaptation, of the security rules can be made through techniques as simpler as generalisation or specialisation of rules, for instance, or by more complex CI methods such as Evolutionary Algorithms.

Another important fact is that MUSES functionalities are completed by a human controller, normally the CSO, who supervises the system activity by means of a graphic interface the CSO can interact with. Thus, adapted and inferred security rules are not directly added to the current set of rules, but they are proposed instead as draft rules to this human controller, in order that they can be accepted if they are interesting and useful. The system also uses the acceptance or rejection of new rules as `feedback`, learning from this decisions, and refining the rules according to this.

The following sections describe these processes: first, focusing on DM techniques to be used both automatically by the MusKRS, and by the mentioned graphic interface for showing useful information to the CSO; second, used CI techniques are explained, mainly focusing in Evolutionary Computation (EC) \cite{EAs_Back96} approaches. EC methods have demonstrated to have a good performance, and have been widely used in security-based environments for solving security issues, such as intrusion detection \cite{GA_intrusion-majeed}, design and evaluation of security protocols \cite{GP_intrusion-lu,GA_networksecurity-zarza}, or for the optimisation of different aspects related with security: IT security costs \cite{EAs_securitycosts-kirta}, and cryptographic protocols \cite{GA_cryptographicprotocols-zarza2}, among others.
